
\section{EXPERIENCE}
\textbf{Senior Engineer} \hfill 2015.1 - present \\
        Elektrobit
        \begin{itemize}  \itemsep -2pt % reduce space between items
        \item UDS and bootloader training.
        \item Developing an AutoSAR CDD (Complex Device Driver) for a BMS (Battery Management System),
              to meaure the voltage of the battery cells.
        \item Adapt and qualify a PSA CAN stack, including CAN driver development and a platform for the qualification,
              transferred how-know from EB France to China.
              Hardware: Cortex-M3 in the STA1085.
        \item Adapt, integrate and qualify a generic bootloader.
              Coordinate and coach local engineers to develop the platform and drivers (CAN and Flash).
              Hardware: TriCore/TC1782.
        \end{itemize}

\textbf{Senior SW Engineer} \hfill 2012.1 - 2014.12\\
        Nokia / Microsoft Mobile
        \begin{itemize}  \itemsep -2pt % reduce space between items
        \item Porting .net framework to Nokia mobile phone;
        Optimized the smarterphone C++ framework;
        Optimized the multi-media library harvester.
        \item Received Nokia AA (achievement award, given to less than 10\% people);
        \item Set up an integration test framework
        and scheduled the tests into CI (continuous integration) system;
        \item Introduced a new way to implement a feature,
        the new way saved the project from delay delivery.
        \end{itemize}

\textbf{Project Manager} \hfill 2008.1 - 2011.12\\
        Elektrobit
        \begin{itemize}  \itemsep -2pt % reduce space between items
            \item City Safety (Automotive): 2010 - 2011
                \begin{itemize} 
                    \item {\em Responsibilities}:
                    I was responsible to coordinate EB experts, customers, and IT supports;
                    and integrate software modules into OSEK OS,
                    including CAN stack, IO driver, bootloader, and XCP.
                    \item {\em Description}:
                    The project was to build a hard realtime system
                    for automobile parking assistance
                    which needs to pay a lot of attention to memory and CPU efficience.
                    The system detects distance via sonar, reads information from automotive BUS network,
                    estimates risk and sends command to other ECUs, such as brake controller.
                    \item {\em Environment}:
                    Windows XP, OSEK OS, MPC5643L, CAN bus
                    \item {\em Tools}:
                    WindRiver Diab Compiler, Lauterbach debugger, EB 6100, Make, EB tresos Studio
                \end{itemize}
            \item TMT (Test Management Tool): 2008 - 2009
                \begin{itemize} 
                    \item {\em Responsibilities}:
                    I was the team lead and architect.
                    The work included requirement collection, design, coding, coordinating and reporting.
                    \item {\em Description}:
                    The project was to create a test management tool
                    which provides test planning, execution and reporting, with a test library.
                    The tool grew to almost 200 thousand lines of code,
                    with 3 servers running together to provide service.
                    The tool distributes computing to browser clients, web server, database and backend server.
                    The team includes 10 persons, including 2 senior developers.
                    \item {\em Environment}:
                    Windows XP/Server , SQLite, SQL Server, Firefox Browser
                    \item {\em Tools}:
                    VIM, Make, MS C++ compiler, WinDbg, Perl, Python, SVN, CVSTrac, doxygen, cxxTest, , Firebug, MS Project
                \end{itemize}
        \end{itemize}
 
\textbf{Software Engineer} \hfill 2005 - 2007 \\
        Elektrobit
        \begin{itemize}  \itemsep -2pt % reduce space between items
            \item {\em TMT (Test Management Tool)}: 2006/04 - 2007/12 \\ 
            I launched the project and worked as the core developer, also drived 
            the project in agile way.
            \item {\em Project Chiron}: 2005/04 - 2006/03 \\
                Testing several smart phones and supported the team with OMA materials.
                The project validated some Symbian phones.
        \end{itemize}
 
\textbf{Software Engineer} \hfill 2000 - 2002 \\
        Several Companies
        \begin{itemize}  \itemsep -2pt % reduce space between items
            \item {\em VoIP Fee}: 2002/04 – 2002/8 \\ 
            The project integrated a GUI with a billing server
            that handles dozens of IP phone calls.
            Multi-threads is used to provide good response to the end user and the VoIP gateways as well.
            \item {\em Search Engine (front end)}:  2001/02 -- 2001/08 \\
                The project makes scalable cluster of full text retrieve servers,
            and provides load-balance for the search request from Internet. 
            \item {\em Image Processing}: 2000/4 - 2000/9\\
                Designed and implemented an image compression algorithm in C/C++ for embedded device.
                Developed a pre-processor to recognize vehicle lisence number and finger-print.
        \end{itemize}
