\section{Why}
I am interested in this position,
including the leading of a team,
technical support to the sales,
facing the customer,
travelling and the interculture communication.
As a project manager, I lead a team to develop OSEKCore (porting and adding some features for local OEM),
and I understood the agreement with customer is very important,
and in some level it determined a project to be successful or how much it can earn.
The Lead Product Expert and his team works together with sales,
and affects the input to projects from technical asepect.
So, this job enables me to contribute more for projects.

Regarding the technology backgroup,
mine spans to many areas although I am now working in CIS.
I led a team to build a WEB based test management tool (TMT),
then I touched the gate of EB Guide for HMI design,
and did pre-sales support regarding the AutoSAR as well.
The sales and I even sold a concept AutoCore license to a China OEM in 2011,
The OEM is still our customer after 6 years.
3 years in Nokia, I was developing phone applications
and UI framework.
Now, I have handled quite a few OSEK projects locally since 2016 spring.
One of my interests is to integrate different technologies
which produce creative solutions.

Already worked with EB France and had fun with my west friends;
for 2 years, supported our Korea agent,
earned their trust and I even learnt a little bit Korean,
found it is not so difficult for a Chinese to understand Korean.
Also, the TMT team was international, including Finnish, Indian, and Chinese colleagues.
All these interculture communication attracted me more and more as time goes by.
