
\section{Experience}
\textbf{Team Manager} \hfill 2022.4.1 - present \\
        Elektrobit Automotive
        \begin{itemize}  \itemsep -2pt % reduce space between items
            \item Recruit and coach a local OS porting team.
            \item Build up local BL team in two sites.
            \item Guide the OSEK team to upgrade the OsekCore to support CanFd, multi-channel and variants.
        \end{itemize}

\textbf{Senior Expert} \hfill 2019.4.1 - 2022.3.31 \\
        Elektrobit Automotive
        \begin{itemize}  \itemsep -2pt % reduce space between items
            \item Support several project managers to lead both OSEK and AUTOSAR projects.
            \item Guide the OSEK team to
            \begin{itemize} \itemsep -2pt
                \item Integrate OSEK LIN stack into AUTOSAR BSW when it does not support LIN slave.
                \item Develop an adaptive flash driver, due to chip supply crisis.
                \item Implement an AUTOSAR module as a sample for local chip vendor.
            \end{itemize}
            \item Enable D-Cache on CortexM chip which does not support cache coherence.
        \end{itemize}

\textbf{Project Manager} \hfill 2016.4.1 - 2019.3.31 \\
        Elektrobit Automotive
        \begin{itemize}  \itemsep -2pt % reduce space between items
        \item Lead several projects in parallel from technical point of view,
            coordinate the teams in different locations,
            make sure the SW product quality and delivery in time.
            Trouble shooting, risk management, and making technical solution as well.
            Scheduling, and training the colleagues to do development and on-site support;
        \item Align BL and OSEK architecture design with headquater,
              and deliver basic software to more than 15 ECUs within half a year;
        \item Customize the OsekCore CAN stack to support E2E protection.
        \item Build up local development force,
        including setting up build servers and labotary,
        coaching new comers
        and leading service team.
        \item Thanks to the exceptional team,
            EB China is now able to offer OSEK products locally.
        \end{itemize}

\textbf{Senior Software Engineer} \hfill 2015.1.9 - 2016.3.31 \\
        Elektrobit Automotive
        \begin{itemize}  \itemsep -2pt % reduce space between items
        \item Provide workshops for China and Korean customers,
            topics:
            XCP/CCP, NM, AutoSAR CanNm, UDS, OEM specific modules, bootloader, etc.
        \item Developing an AutoSAR CDD (Complex Device Driver) for a BMS (Battery Management System),
            to meaure the voltage of the battery cells.
        \item Adapt and qualify several CAN/LIN stacks and bootloaders.
            including CAN/LIN, flash driver porting, integration, and testing.
            transferred how-know from EB France to China.
            Hardware: Cortex-M3/STA1085, PA, S12x, Ti/TMS320, RL78, RH850, TriCore, PIC24, MB96, etc.
        \end{itemize}

\textbf{Senior Software Engineer} \hfill 2012.1.4 - 2014.12.30 \\
        Nokia
        \begin{itemize}  \itemsep -2pt % reduce space between items
                \item Porting MS .net micro framework to Nokia mobile phone, based on the smarterphone framework.
        \item Accomplished a lot of development tasks, including:
            optimized smarterphone framework and middleware, added some components / features, and fixed bugs,
        on Nokia mobile phones.
        % .net framework to Nokia mobile phone;
        % Optimized the smarterphone C++ framework;
        % Optimized the multi-media library harvester.
        \item More than a developer 
            \begin{itemize}  \itemsep -2pt
                \item Launched an integration test project to guard code changes
                with scheduled tests in CI (continuous integration) system;
                \item Provided some lectures about CBD (contract based development) and
                TDD (test driven development) via practical examples;
                \item Improved the auto documentation of source code;
                \item Coordinated the developers, testers and UX (user experience) designers for 3 new features.
            \end{itemize}
        \item All these works resulted in a Nokia AA (achievement award, given to less than 10\% people);
        \end{itemize}

\textbf{Senior Software Engineer} \hfill 2008.1.1 - 2011.12.31 \\
        Elektrobit Wireless
        \begin{itemize}  \itemsep -2pt % reduce space between items
            \item {\em AUTOSAR Technical Support}: 2011 \\
                    Provided pre-sales technical support
                    and turned out to win an order of AUTOSAR basic software together with configuration tool.
            \item {\em City Safety (Automotive ECU)}: 2010 - 2011 \\
                    optimized the bootloader from downloading in minutes to within a minute;
                    also coordinated EB experts, customers, IT supports, etc.
            \item {\em HMI and ECU trainings}: 2010\\
                Organized and received 2 trainings about HMI design and OSEK/AUTOSAR.
            \item {\em TMT (Test Management Tool)}: 2008 - 2009 \\
                    Lead the team in agile way
                    to create a web based, but native UI looked, test management tool (TMT)
                    that supports test planning, execution and reporting.
                    Met the schedule and updated the server online every 2 weeks.
        \end{itemize}
 
\textbf{Software Engineer} \hfill 2005.4.18 - 2007.12.31 \\
        Elektrobit Technology
        \begin{itemize}  \itemsep -2pt % reduce space between items
            \item {\em TMT (Test Management Tool)}: 2006/04 - 2007/12 \\ 
            I launched the project and worked as the core developer, also drove
            the project in agile way.
            \item {\em Project Chiron}: 2005/04 - 2006/03 \\
                Testing several smart phones and supported the team with OMA materials.
                The project validated some Symbian phones.
        \end{itemize}
 
\textbf{Software Engineer} \hfill 2000.4.1 - 2002.08.21 \\
        TRS Technology
        \begin{itemize}  \itemsep -2pt % reduce space between items
            \item {\em Site Search Engine} \\ 
                Serach Engine front-end design and implementation.
                The engine ranged to one or several web sites, based on JSP/Servlet and full text retrieve servers (TRS).
                Tried to do load balance with a cluster of servers.
        \end{itemize}
