
\section{EXPERIENCE}
\textbf{Senior SW Engineer / Project Coordinator} \hfill 2012.1 - present \\
        Nokia, Microsoft
        \begin{itemize}  \itemsep -2pt % reduce space between items
        \item Accomplished a lot of development tasks, including:
            porting .net to Nokia mobile phone, optimized smarterphone framework and middleware, added some components / features,
            and fixed many bugs on Nokia mobile phones.
        % .net framework to Nokia mobile phone;
        % Optimized the smarterphone C++ framework;
        % Optimized the multi-media library harvester.
        \item More than a developer 
            \begin{itemize}  \itemsep -2pt
                \item Coordinated the developers, testers and UX (user experience) designers to implement 3 new features.
                \item Launched an integration test project to guard code changes
                with scheduled tests in CI (continuous integration) system;
                \item Served some lectures about CBD (contract based development) and
                TDD (test driven development) via practical examples;
            \end{itemize}
        % \item Understood the matrix of a larger development team;
        \item All these works resulted in a Nokia AA (achievement award, given to less than 10\% people);
        \end{itemize}

\textbf{Project Manager} \hfill 2008 - 2011\\
        Elektrobit
        \begin{itemize}  \itemsep -2pt % reduce space between items
            \item {\em AUTOSAR Technical Support}: 2011 \\
                    Provided pre-sales technical support
                    and turned out to win an order of AUTOSAR base software together with development tools.
                    The deal encouraged our boss to pay bonus even when I was leaving.
            \item {\em City Safety (Automotive ECU)}: 2010 - 2011 \\
                    Coordinated EB experts, customers, IT supports, and managers.
                    Involved to integrate software modules into OSEK OS,
                    including CAN stack, IO driver, bootloader, and XCP;
            \item {\em HMI and ECU trainings}: 2010\\
                Organized and received 2 trainings about HMI design and OSEK/AUTOSAR.
            \item {\em TMT (Test Management Tool)}: 2008 - 2009 \\
                    Led the project in customized agile way,
                    to create a web based test management tool
                    that supports test planning, execution and reporting.
                    The team was distributed in 2 cities,
                    and included 10 software engineers who came from Finnish, India and China.
                    The project met the schedule by updating the server online every 2 weeks.
        \end{itemize}
 
\textbf{Software Engineer} \hfill 2005 - 2007 \\
        Elektrobit
        \begin{itemize}  \itemsep -2pt % reduce space between items
            \item {\em TMT (Test Management Tool)}: 2006/04 - 2007/12 \\ 
            I launched the project and worked as the core developer, also drove
            the project in agile way.
            \item {\em Chiron}: 2005/04 - 2006/03 \\
                Testing several smart phones and supported the team with OMA/DRM materials.
                The project validated some Symbian phones.
        \end{itemize}
 
\textbf{Software Engineer} \hfill 2000 - 2002 \\
        Several Companies
        \begin{itemize}  \itemsep -2pt % reduce space between items
            \item {\em VoIP Fee}: 2002/04 – 2002/08 \\ 
            The project developed a GUI application, which is, at the same time, a billing server
            that handles dozens of IP phone calls.
            Multi-thread is used to provide good response to the end user and the VoIP gateways as well.
            \item {\em Search Engine (front end)}:  2001/02 -- 2001/08 \\
                The project makes scalable cluster of full text retrieve servers,
            and provides load-balance for the search requests from Internet. 
            \item {\em Image Processing}: 2000/04 - 2000/09\\
                Designed and implemented an image compression algorithm in C/C++ for embedded device.
                Developed a pre-processor, as the first step,
                to recognize vehicle lisence number and human finger-print.
        \end{itemize}
